### 2020-01-23 CalNotes.tex
Partial

\section{The one-dimensional case}

Let us consider $N = 1$ and write $A_1 = A$ and $V_1 = V$, respectively. The posterior distribution of $A$ given a trajectory $(X_t, 0 \leq t \leq T)$ is in this case a Gaussian $\mathcal N(\bar A_T, \sigma^2_T)$ where
\begin{equation}
\begin{aligned}
	\bar A_T &= \frac{A_0}{1+\sigma_0^2\int_0^T V'(X_t)^2 \dd t} - \frac{\sigma_0^2\int_0^T  V'(X_t) \dd X_t}{1+\sigma_0^2\int_0^T V'(X_t)^2 \dd t}, \\
	\sigma^{-2}_T &= \sigma_0^{-2} + \int_0^T V'(X_t)^2 \dd t.
\end{aligned}
\end{equation}
We will in the following sections analyse the convergence of the posterior, both in case data from the multiscale process is not treated and in case they are pre-processed.

\subsection{A filtering approach}

>>>>

\section{A filtering approach}

%Let us consider $N = 1$ and write $A_1 = A$ and $V_1 = V$, respectively. The posterior distribution of $A$ given a trajectory $(X_t, 0 \leq t \leq T)$ is in this case a Gaussian $\mathcal N(\bar A_T, \sigma^2_T)$ where
%\begin{equation}
%\begin{aligned}
%	\bar A_T &= \frac{A_0}{1+\sigma_0^2\int_0^T V'(X_t)^2 \dd t} - \frac{\sigma_0^2\int_0^T  V'(X_t) \dd X_t}{1+\sigma_0^2\int_0^T V'(X_t)^2 \dd t}, \\
%	\sigma^{-2}_T &= \sigma_0^{-2} + \int_0^T V'(X_t)^2 \dd t.
%\end{aligned}
%\end{equation}
%We will in the following sections analyse the convergence of the posterior, both in case data from the multiscale process is not treated and in case they are pre-processed.
